Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-07 paper/main.tex
completely remove multilayer stuff from paper
use new paths for figures

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.54\textwidth]
        {figures/crm_fit/snapshots/predicted-031111.png}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.41\textwidth]
        {figures/crm_fit/celldifss/cell-031111.png}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \caption{
        \textbf{TODO do we need this figure?}
        (A) A microscopic image with the predicted positions of the cells overlayed on top.
        (B) Differences between extracted and predicted positions.
        % TODO make this figure to scale
    }
    \label{fig:celldiffs-individual}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/damping.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/exponent-m.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/exponent-n.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/strength.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-0.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-0.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
    \end{tikzonimage}
    \caption{
        Sensitivity analyses werer performed for every optimized parameter of our model.
        (A-F) show the curves of loss functions when varying this respective parameter and keeping
        all others constant at the value of the found optimum (blue dot).
        In the cases of (B-F), we can see that a minimum was achieved and thus the parameters could
        be estimated.
        However, for the case of the damping constant $\lambda$ in (A), we see that the upper bound
        is open.
        This suggests that our model could be reduced with regard to this parameter.
        We have exemplified the values for radii $r_i$ and growth rates $\mu_i$ with values of the
        first cell.
        The remaining plots can be found in the supplementary material in
        section~\ref{sec:supplement-parameter-profiles}.
    }
    \label{fig:parameter-estimates-single-step}
\end{figure}

@@

%###################################################################################################
% \subsection{Multilayer Predictions}
% % TODO
%
% \begin{itemize}
%     \item Friction force against surface. perpendicular to motion; proportional to velocity.
%     \item gel pressure coming from experiment (simply downwards force $F_z$)
% \end{itemize}
%
% \begin{itemize}
%     \item Do we need this in this publication?
%     \item Maybe this is out of scope as this is a more methodological paper.
%     \item If we want to omit it, we might also opt to change the model description in the beginning
%         and remove some parts of the external forces discussion.
% \end{itemize}
%
% \cite{You2019}
%
% \begin{figure}
%     \centering
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_multilayer/multilayer-time-evolution.pdf}\\
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_multilayer/colony-height-vs-gel_pressure.pdf}
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_multilayer/colony-height-vs-time.pdf}
%     \caption{TODO}
%     \label{fig:multilayer}
% \end{figure}

>>>>

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.49\textwidth]
        {figures/crm_fit/snapshots/predicted-001667.png}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.49\textwidth]
        {figures/crm_fit/celldiffs/diff-001667.png}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \caption{
        \textbf{TODO do we need this figure?}
        (A) A microscopic image with the predicted positions of the cells overlayed on top.
        (B) Differences between extracted and predicted positions.
        % TODO make this figure to scale
    }
    \label{fig:celldiffs-individual}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/damping.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/exponent-m.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/exponent-n.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/strength.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-0.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
    \end{tikzonimage}
    \caption{
        Sensitivity analyses werer performed for every optimized parameter of our model.
        (A-F) show the curves of loss functions when varying this respective parameter and keeping
        all others constant at the value of the found optimum (blue dot).
        In the cases of (B-F), we can see that a minimum was achieved and thus the parameters could
        be estimated.
        However, for the case of the damping constant $\lambda$ in (A), we see that the upper bound
        is open.
        This suggests that our model could be reduced with regard to this parameter.
        We have exemplified the values for radii $r_i$ and growth rates $\mu_i$ with values of the
        first cell.
        The remaining plots can be found in the supplementary material in
        section~\ref{sec:supplement-parameter-profiles}.
    }
    \label{fig:parameter-estimates-single-step}
\end{figure}

@@
